Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-09 draft.tex
Put affiliations into a separate file

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
    \input{authors.tex}
  \end{small}
\begin{footnotesize}
  \vspace{2mm}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France --
          Institut des Maladies Neurodégénératives, Université de Bordeaux,
          CNRS UMR 5293, Bordeaux, France -- 
          LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS UMR 5800, Talence, France •
    $^{2}$Centre de Biophysique Moléculaire,
          CNRS UPR4301, Orléans --
          Synchrotron SOLEIL, Division Expériences,
          Gif sur Yvette, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}

>>>>

\title{Long-Term Reproducibility through Replication:\\
       the ReScience Initiative}
\author{%
  \begin{small}
    \input{authors.tex}
  \end{small}
\begin{footnotesize}
  \vspace{2mm}
  \input{affiliations.tex}
  $^{*}$Corresponding author:
        \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}          
  \end{footnotesize}
}
